Reassessing the Impact of Dynamic Slicing in SFL

### 2019-02-01 paper/ijcai/paper.tex
pass on intro

Dynamic Slicing (\ds{}) and Spectrum-Based Fault Localization (\sfl{})
are two very popular techniques that use different principles to
automate debugging. Dynamic Slicing~\cite{Agrawal:1990:DPS:93542.93576} looks for the statements
in code that influence the evaluation of the fault-revealing
assertion. Although the technique has been intensively investigated in
research, few use cases gained notoriety---WhyLine~\cite{Ko:2008:DRA:1368088.1368130} being an
exception. In contrast to \ds{}, \sfl{}~\cite{7390282} does not analyze
code. It is a black-box~
statistical fault localization method that computes suspiciousness
values associated with program entities (e.g., basic blocks). For
that, it uses coverage information of passing and failing test
cases. \sfl{} produces a list of program entities ranked in decreasing
order of suspiciousness. Similarly to \ds{}, \sfl{} received
tremendous attention over the years, but its applicability to support
debugging remains
questionable~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}.
Despite the skepticism of the research community, \sfl{} has been
shown useful in supporting downstream analyses, such as Automated
Program Repair
(\apr{})~\cite{automatic-software-repair-survey2017,kim-etal-daghstul2017},
an increasingly popular technique that looks for fixes to buggy
statements. Tools like JAFF \cite{arcuri-2011}, Prophet
\cite{long-rinard-2016}, SemFix \cite{nguyen-qi-roychoudhury-2013},
and SPR \cite{long-rinard-2015} use \sfl{} to guide the search for
likely fixes.

\ds{} and \sfl{} are complementary. Intuitively, \ds{} identifies
irrelevant parts of the code whereas \sfl{} ranks the relevant parts
of the code.  This paper reports the results of a comprehensive study
to evaluate the impact of \ds{} to improve \sfl{}. The study involves
\numFaults{} faults from \numPrograms{} programs from the Defects4J (D4J)
dataset~\cite{just-defects4j-issta2014}, which is frequently used to
evaluated fault localization research. The intuition for the \comb{}
combination is that several highly ranked statements, albeit covered
by failing executions, may be unrelated to the fault. Prior work
reported promising results in this combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}.
We found surprising that, despite these findings, no tool or client analyses use this combination
today.\Sof{@todo: Revise this and look to the paper from 2018} Several reasons could justify that observation. One hypothesis is that results reported in prior work are
over-optimistic. For example, most prior work evaluated improvements
of \sfl{} techniques using relative metrics, which are based on the
position of the first faulty statements found in the ranking relative
to the total number of ranked statements, which is often a large
number. As such, it inflates actual improvements and deceives
potential adopters of the technology. Ang \etal~\cite{ang-perez-van-deursen-rui-2017} recently
pointed to that fact and encouraged researchers to adopt more precise metrics,
such as \topk{}
\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359},
which has been widely adopted to evaluate performance of information retrieval algorithms~\Fix{cite}. This
metric reports the percentage of faults captured by a technique when
the rank is trimmed to the first $k$ components.

The goal of this paper is to reassess whether the \comb{} combination
is worthwhile under the light of a more accurate metric and a larger
dataset. The D4J dataset is about twice as large than the biggest test
suite used in previous studies. It is worth noting that \acrAbrev{}
techniques should directly benefit from these results---either to
improve their results or to be aware they should not invest on this
integration. This study covers the following research questions:

>>>>

%% Although the technique has been intensively investigated in
%% research, few use cases gained notoriety---WhyLine~\cite{Ko:2008:DRA:1368088.1368130} being an
%% exception.

Dynamic Slicing (\ds{}) and Spectrum-Based Fault Localization (\sfl{})
are two very popular techniques that use different principles to
automate debugging. Dynamic
Slicing~\cite{Agrawal:1990:DPS:93542.93576} looks for the statements
in code that influence some point of interest, such as the evaluation
of a failing assertion. In contrast to \ds{}, \sfl{}~\cite{7390282}
does not analyze code. It is a black-box statistical fault
localization method that computes suspiciousness values associated
with program entities (e.g., basic blocks) based on coverage and the
output of test cases. More precisely, \sfl{} uses coverage information
of passing and failing test cases to identify likely faulty
statements. It produces on output a list of program entities ranked in
decreasing order of suspiciousness.
\ds{} and \sfl{} are complementary debugging techniques. Intuitively, \ds{} identifies
irrelevant parts of the code whereas \sfl{} ranks the relevant parts
of the code.

%% Similarly to \ds{}, \sfl{} received
%% tremendous attention in research over the years,
%% but its applicability to support
%% debugging remains
%% questionable~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}.
%% Despite the skepticism of the research community, \sfl{} has been
%% shown useful in supporting downstream analyses, such as Automated
%% Program Repair
%% (\apr{})~\cite{automatic-software-repair-survey2017,kim-etal-daghstul2017},
%% an increasingly popular technique that looks for fixes to buggy
%% statements. Tools like JAFF \cite{arcuri-2011}, Prophet
%% \cite{long-rinard-2016}, SemFix \cite{nguyen-qi-roychoudhury-2013},
%% and SPR \cite{long-rinard-2015} use \sfl{} to guide the search for
%% likely fixes.

%% We found surprising that, despite these findings, no tool or client analyses use this combination
%% today.\Sof{@todo: Revise this and look to the paper from 2018} Several reasons could justify that observation. One hypothesis is that results reported in prior work are
%% over-optimistic. For example, most prior work evaluated improvements
%% of \sfl{} techniques using relative metrics, which are based on the
%% position of the first faulty statements found in the ranking relative
%% to the total number of ranked statements, which is often a large
%% number. As such, it inflates actual improvements and deceives
%% potential adopters of the technology. Ang \etal~\cite{ang-perez-van-deursen-rui-2017} recently
%% pointed to that fact and encouraged researchers to adopt more precise metrics,
%% such as \topk{}
%% \cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359},
%% which has been widely adopted to evaluate performance of information retrieval algorithms~\Fix{cite}. This
%% metric reports the percentage of faults captured by a technique when
%% the rank is trimmed to the first $k$ components.

This paper reports the results of a comprehensive study
to evaluate the impact of \ds{} to improve \sfl{}. The study involves
\numFaults{} faults from \numPrograms{} programs from the Defects4J
(D4J) dataset~\cite{just-defects4j-issta2014}, which is frequently
used to evaluated fault localization research. The intuition for the
\comb{} combination is that several highly ranked statements, albeit
covered by failing executions, may be unrelated to the fault. Prior
work reported promising results in this
combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}
but they used non-representative set of subjects in their evaluation
or used less rigorours methods to assess improvement of techniques compared to those used
today~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}.
The goal of this paper is to reassess whether the \comb{} combination
is worthwhile under the light of a more accurate metric and a larger
dataset. The D4J dataset is about twice as large than the biggest test
suite used in previous studies. It is worth noting that \acrAbrev{}
techniques should directly benefit from these results---either to
improve their results or to be aware they should not invest on this
integration. This study covers the following research questions:
